\textbf{Response Letter}

### 2018-12-25 doc/aij18/major-revision/letter.tex
Update Dec 25 at 12.20
Update Dec 25 at 13.00

\textcolor{blue}{The post-processing is applied to learning preconditions that are static literals and are never deleted or added. We inherit the same procedure for learning preconditions presented in [40]. The pseudo-code is presented in [40] (algorithm 2). }

\textcolor[rgb]{1.00,0.00,0.50}{\textbf{PENDIENTE DIEGO MIRE UNA FRASE QUE LE HE MANDADO POR EMAIL}}

@@

\textcolor[rgb]{1.00,0.00,0.00}{NO ESTA HECHO TODAVIA}

>>>>

\textcolor{blue}{We have added a new sentence that overviews the post-process. We have also rephrases some part of the text to make it more comprehensible. We believe the text provides now a clear idea of the post-process and that the pseudo-code is not necessary. Nevertheless, we refer the reviewer to the pseudo-code presented in [40] (algorithm 2) for a more detailed explanation.}

@@
